Universal Anonymous Signatures

### 2022-07-26 prism-backend/research/gsac/relationships.tex
Migrating from fissue being a predicate to it being a function.

  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \textbf{Issuance functions:}
      \begin{align}
        & \fissue^1(\cdot,\cdot,\cdot) \coloneqq 1 \nonumber \\
        & \fissue^{single,L}((\upk,\cdot),\cdot,\cdot) \coloneqq
          \pcreturn \upk \notin L
          \nonumber \\
        & \fissue^{\sring}((\upk,\cdot),\attrs,\cdot) \coloneqq
          \pcreturn (\attrs \subseteq \sring \land \upk \in \sring) \nonumber \\
        & \fissue^{l,\dattrs}(\cdot,\attrs,(\cid,\cattrs)) \coloneqq
          \pcreturn (\attrs_1 = l+1 \land \attrs \subseteq
          \lbrace \cattrs_i \rbrace_{i\in\dattrs}) \nonumber
      \end{align}

      \textbf{Signature evaluation functions:}
      \begin{align}
        & \feval^0(\cdot,\cdot,\cdot) \coloneqq \pcreturn (0,\ast) \nonumber \\
        & \feval^{\dattrs}(\cdot,(\cid,\attrs),\cdot)
          \coloneqq \pcreturn (\lbrace \attrs_i \rbrace_{i\in \dattrs},\ast)
          \nonumber \\
        & \feval^{\sring}((\upk,\cdot),(\cid,\attrs),\cdot)
          \coloneqq \pcif \upk \in \attrs:
          \pcreturn (\attrs,\ast);
          \pcelse \pcreturn \bot \nonumber \\
        & \feval^{l,\dattrs}(\cdot,(\cid,\attrs),\cdot) \coloneqq
          \pcreturn((\attrs_1,\lbrace\attrs_i\rbrace_{i\in\dattrs}),\ast)
          \nonumber
      \end{align}
    \end{minipage}
  }
  \vspace*{1em}

  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \textbf{Open functions:}
      \begin{align}
        & \finsp^0(\cdot,\cdot,\cdot,\cdot) \coloneqq 0 \nonumber \\
        & \finsp^{\upk}(\cdot,(\upk,\cdot),\cdot,\cdot) \coloneqq
          \pcreturn \upk % \CCommit(\usk;0)
          \nonumber
      \end{align}
    \end{minipage}
    \hspace*{5em}
    % \begin{minipage}[t]{0.47\textwidth}
    %   \begin{framed}
    %     $\attrs(\cred)$ returns all attributes in \cred \\
    %     $\dattrs(\cred)$ returns $\dattrs \subseteq \attrs(\cred)$ \\
    %     $\attrs_i(\cred)$ returns $i$-th attribute in \cred \\
    %     $\ast$ means the output is ignored \\
    %     $\bot$ means the function fails
    %   \end{framed}
    % \end{minipage}
  }
  \caption{Functions for the \CUASGen restrictions described next.
    For readability, we use ``$\cdot$'' to denote input arguments that are
    ignored; and ``$\ast$'' to denote output values that can be set to anything
    (but should be ignored). $\bot$ means the function fails.}
    % $\attrs(\cred)$ returns all attributes in \cred. $\dattrs(\cred)$ returns
    % $\dattrs \subseteq \attrs(\cred)$. $\attrs_i(\cred)$ returns $i$-th
    % attribute in \cred. $\ast$ means the output is ignored (in these examples,
    % we use this to mean that $\yeval^1$ is unused. $\bot$ means the function
    % fails.}
  \label{fig:func-restrictions}
\end{figure}

@@

\subsubsection{\CUASRing Construction.} %
Building a ring signature scheme according to the model in \figref{fig:model-rs}
is essentially a $(\fissue^{\sring},\feval^{\sring},\finsp^0)$-restriction of
our $\CUASGen^{hide-iss}$ construction. Concretely, for any desired ring, the
signer (who is also the issuer) simply must set $\sipk=\sring$. The construction
is as follows:

@@

\begin{description}
%\item[$\parm \gets \Setup(\secpar,\AttrSpace)$.] As in $\CUASGen^{hide-iss}$.
\item[$((\pk_1,\sk_1),...,(\pk_n,\sk_n)) \gets KeyGen(\secpar)$.] Runs
  $\parm \gets \Setup(\secpar)$ from $\CUASGen^{hide-iss}$, as well as $n$
  instances of $(\ipk_i,\isk_i) \gets \IKeyGen(\parm,\fissue^{\sring})$, and
  $(\opk,\osk) \gets \OKeyGen(\parm,\finsp^0)$.
  \jesus{This syntax restricts to fixing the rings at setup time. But the
    RS syntax in \cite{bkm06} is also somehow static already, in that it does
    not allow adding users on the fly. Is it ok?}
\item[$\langle \cred,\bot,\utrans,\bot \rangle \gets
  \langle \Obtain(\usk,\scred,\attrs),\Issue(\isk,\sipk,\attrs)\rangle.$]
  A user, with $\usk=\isk_i$ and $\upk=\ipk_i$ for some $i \in [n]$, self-issues
  to itself a credential for the ring \sring chosen at setup time. Then, runs
  the $\langle \Obtain,\Issue \rangle$ protocol as in $\CUASGen^{hide-iss}$,
  acting both as user and as issuer, using $\fissue^{\sring}$ as issuance
  function, and $\attrs \gets \sring$.
\item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\cred,\msg,\feval).$] As in
  $\CUASGen^{hide-iss}$, using $\feval^{\sring}$ as sign evaluation function,
  using as signing credential the self-issued credential.
\item[$1/0 \gets \Verify(\opk,\sipk,\sig,\yeval,\msg,\feval).$] As in
  $\CUASGen^{hide-iss}$. Note that $\sipk=\sring$, and $\feval=\feval^{\sring}$.
% \item[$\Open$ and $\Judge$.] As in $\CUASGen^{\Sign-prv}$. Note that
%   $\finsp=\finsp^0$.
\end{description}

>>>>

  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \textbf{Issuance functions:}
      \begin{align}
        & \fissue^1(\cdot,\cdot,\cdot) \coloneqq 1 \nonumber \\
        & \fissue^{single,L}(\upk,\cdot,\cdot) \coloneqq
          \pcreturn \upk \notin L
          \nonumber \\
        & \fissue^{\sring}(\upk,\attrs,\cdot) \coloneqq
          \pcreturn (\attrs = \sring \land \upk \in \attrs) \nonumber \\
        & \fissue^{l,\dattrs}(\cdot,\attrs,(\cid,\cattrs)) \coloneqq
          \pcreturn (\attrs_1 = l+1 \land \attrs \subseteq
          \cup_{i\in\dattrs} \cattrs_i) \nonumber
      \end{align}

      \textbf{Signature evaluation functions:}
      \begin{align}
        & \feval^0(\cdot,\cdot,\cdot) \coloneqq \pcreturn (0,\ast) \nonumber \\
        & \feval^{\dattrs}(\cdot,(\cid,\attrs),\cdot)
          \coloneqq \pcreturn (\lbrace \attrs_i \rbrace_{i\in \dattrs},\ast)
          \nonumber \\
        & \feval^{\sring,\dattrs}(\upk,(\cid,\attrs),\cdot)
          \coloneqq \pcif \upk \in \lbrace \attrs_i \rbrace_{i\in\dattrs}
          \subseteq \sring:
          \pcreturn (\lbrace \attrs_i \rbrace_{i\in\dattrs},\ast);
          \pcelse \pcreturn \bot \nonumber \\
        & \feval^{l,\dattrs}(\cdot,(\cid,\attrs),\cdot) \coloneqq
          \pcreturn((\attrs_1,\lbrace\attrs_i\rbrace_{i\in\dattrs}),\ast)
          \nonumber
      \end{align}
    \end{minipage}
  }
  \vspace*{1em}

  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \textbf{Open functions:}
      \begin{align}
        & \finsp^0(\cdot,\cdot,\cdot,\cdot) \coloneqq 0 \nonumber \\
        & \finsp^{\upk}(\cdot,\upk,\cdot,\cdot) \coloneqq
          \pcreturn \upk % \CCommit(\usk;0)
          \nonumber
      \end{align}
    \end{minipage}
    \hspace*{5em}
    % \begin{minipage}[t]{0.47\textwidth}
    %   \begin{framed}
    %     $\attrs(\cred)$ returns all attributes in \cred \\
    %     $\dattrs(\cred)$ returns $\dattrs \subseteq \attrs(\cred)$ \\
    %     $\attrs_i(\cred)$ returns $i$-th attribute in \cred \\
    %     $\ast$ means the output is ignored \\
    %     $\bot$ means the function fails
    %   \end{framed}
    % \end{minipage}
  }
  \caption{Functions for the \CUASGen restrictions described next.
    For readability, we use ``$\cdot$'' to denote input arguments that are
    ignored; and ``$\ast$'' to denote output values that can be set to anything
    (but should be ignored). $\bot$ means the function fails.}
    % $\attrs(\cred)$ returns all attributes in \cred. $\dattrs(\cred)$ returns
    % $\dattrs \subseteq \attrs(\cred)$. $\attrs_i(\cred)$ returns $i$-th
    % attribute in \cred. $\ast$ means the output is ignored (in these examples,
    % we use this to mean that $\yeval^1$ is unused. $\bot$ means the function
    % fails.}
  \label{fig:func-restrictions}
\end{figure}

@@

\subsubsection{\CUASRing Construction.} %
Building a ring signature scheme according to the model in \figref{fig:model-rs}
is essentially a $(\fissue^{\sring},\feval^{\sring,\dattrs},\finsp^0)$-restriction
of our $\CUASGen^{hide-iss}$ construction. The construction is as follows:

@@

\begin{description}
%\item[$\parm \gets \Setup(\secpar,\AttrSpace)$.] As in $\CUASGen^{hide-iss}$.
\item[$((\pk_1,\sk_1),...,(\pk_n,\sk_n)) \gets KeyGen(\secpar)$.] Runs
  $\parm \gets \Setup(\secpar)$ from $\CUASGen^{hide-iss}$, as well as $n$
  instances of $(\ipk_i,\isk_i) \gets \IKeyGen(\parm,\fissue^{\sring})$, where
  $\sring = \lbrace \ipk_i \rbrace_{i\in[n]}$, and $(\opk,\osk) \gets
  \OKeyGen(\parm,\finsp^0)$. 
\item[$\langle \cred,\bot,\utrans,\bot \rangle \gets
  \langle \Obtain(\usk,\scred,\attrs),\Issue(\isk,\sipk=\attrs,\attrs)\rangle.$]
  A user, with $\usk=\isk_i$ and $\upk=\ipk_i$ for some $i \in [n]$, acts both
  as user and issuer to self-issue a credential for an attribute set \attrs such
  that $\attrs \subseteq \sring$, where \sring is the set of public keys used to
  define $\fissue^{\sring}$.
\item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\cred,\msg,\feval).$] As in
  $\CUASGen^{hide-iss}$, using $\feval^{\sring,\dattrs}$ as evaluation
  function, using as signing credential the self-issued credential. Note that
  $\dattrs \subseteq \attrs = \sring$ defines the subring to use for the
  produced signature.
\item[$1/0 \gets \Verify(\opk,\sipk,\sig,\yeval,\msg,\feval).$] As in
  $\CUASGen^{hide-iss}$, making $\sipk=\yeval=\lbrace \ipk_i
  \rbrace_{i\in\dattrs}$.
\end{description}

%Note that by using, e.g., $\finsp^{\upk}$, we essentially get a ring signature
%scheme with linkability via an opener.
